---
title: "WBG Energy Efficiency Portfolio Analysis"
author: "Aline"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  html_document: default
  pdf_document: default
  word_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,fig.retina = 2, fig.width = 7, fig.height = 6, message=FALSE,warning=FALSE)

.libPaths("C:/Users/wb500886/Downloads/library")
# load package
library(sjPlot)
library(sjmisc)
library(sjlabelled)

library(plm)
library(lfe)
library(broom)

library(skimr)
library(tibble)
library(tidyverse)
library(stargazer)
library(knitr)
library(kableExtra)
library(forcats)
library(readxl)
library(openxlsx)
library(countrycode)
library(corrplot)

library(RColorBrewer)
library(imputeTS)

library(officer)
library(rvg)

library(janitor)
```


```{r data}

#load data-----
load("data/ee_wb.rda")
load("data/operation_0.rda")
load("data/wb_kw.rda")
load("data/fcv.rda") #should use the historical list. 
load("data/sector.rda")
load("data/rise.rda")
load("data/ctr_ptf.rda")
load("data/ctr_tag.rda")

#variables needed-----
var_keep_ifc <- c("pid", "name","rgn", "ctr", "appfy", "income", "appfy", "inst","amount(m)","sector_1","sector_2","sector_3")

#ifc status-----
ifc_status <- read_excel("input/ifc/Project Extract as of 0430201.xlsx") %>%
  select(`Project ID`,`Project Status Name`) %>%
  rename(pid = `Project ID`,
         status = `Project Status Name`) %>%
  rbind( read_excel("input/ifc/AS-1.12_-_Key_Memo_Details_for_Projects 063020.xlsx") %>%
               select(`Project ID`,`Project Status`) %>%
               rename(pid = `Project ID`,
                      status = `Project Status`)) %>%
  mutate(status = toupper(status))

#clean the ee_ifc -----
ee_ifc_raw <- read_excel("input/EE_IFC_projects_0930.xlsx")
test<-anyDuplicated(ee_ifc_raw$PID)

ee_ifc_use <- ee_ifc_raw %>%
  rename(source = Source,
         pid = PID,
         name = project_name)%>%
  select(var_keep_ifc) %>%
  mutate(income = recode(income,
                         L = "LIC",
                         H = "HIC",
                         LM = "LMIC",
                         UM = "UMIC")) %>%
  distinct() %>%
  left_join(ifc_status, by = "pid")

test<-anyDuplicated(ee_ifc_use$pid)
test<-skim(ee_ifc_use)

test <- ee_ifc_use %>% 
  filter(is.na(income)) %>% 
  distinct(ctr)




#WBG EE profile-----
ee_wbg <- ee_wb %>%
  select(-iso3c)%>%
  plyr::rbind.fill(ee_ifc_use) %>%
  mutate(`amount(m)` = round(`amount(m)`,digits = 2)) %>%
  mutate(inst_grp = case_when(grepl("IFC",inst) ~ "IFC",
                              grepl("WB", inst) ~ "WB" )) %>%
  mutate(type = case_when(grepl("IS|Lend",inst) ~ "IS",
                          TRUE ~ "AS"),
         appfy = as.character(appfy)) %>%
  select(pid,inst,rgn,ctr,income,appfy,`amount(m)`,everything()) %>%
  #left_join(fcv,by = c( "ctr" = "CNTRY_SHORT_NAME", "appfy" = "PROJ_APPRVL_FY" )) %>%
  #rename(fcv = FRAGILE_STATE_IND) %>% 
  mutate(ctr_code = countrycode(ctr, 
                           origin = 'country.name',
                           destination = 'iso3c',
                           custom_match = c('Kosovo'='KVO',
                                            "Yemen, People's Democratic Republic of" = 'YEM'))) %>%
  left_join(ctr_tag %>% select(FCS,iso3c,`Income Level`,fy) %>%
              mutate(fy = as.character(fy)), by =c("ctr_code"="iso3c","appfy"="fy"))%>%
  #mutate(fcv = ifelse(is.na(fcv)&!is.na(ctr_code),FCS,fcv),
  #       fcv = toupper(fcv),
  #      income = ifelse(is.na(income)&!is.na(ctr_code),`Income Level`,income)) %>%
  #select(-FCS,-`Income Level`)

```

```{r quality, results='hide',fig.show='hide',echo=FALSE,message=FALSE}
anyDuplicated(ee_wbg$Pid)
skim(ee_wbg)

ee_wbg %>% 
  filter(is.na(fcv)) %>%
  filter(!is.na(appfy),
         !grepl("Region",ctr))%>%
  distinct(ctr,appfy) #good

ee_wbg %>% 
  filter(is.na(income))%>%
  filter(!is.na(appfy),
         !grepl("Region|World",ctr))%>%
  distinct(ctr,appfy) #Serbia 2007 missing in ee_ifc_use but fixed in ee_wbg.

ee_wbg %>% 
  filter(is.na(ctr_code),
         !grepl("Region|World",ctr))%>%
  distinct(ctr) #good. 

ee_ifc_use %>%
  filter(dplyr::between(appfy,2011,2020))%>%
  nrow()

ee_wbg %>%
  filter(grepl("IFC",inst))%>%
  filter(dplyr::between(appfy,2011,2020))%>%
  nrow()

save(ee_wbg, file ="data/ee_wbg.rda")

#outprint to excel
ee_wbg %>%
  select(-type,-inst_grp) %>%
  arrange(inst,rgn,ctr,appfy)%>%
  openxlsx::write.xlsx("output/EE_WBG_1023.xlsx", sheetName = "EE_WBG", firstRow = TRUE, firstCol = TRUE)

ee_wbg %>%
  select(-type,-inst_grp) %>%
  arrange(inst,rgn,ctr,appfy)%>%
  filter(grepl("WB",inst,ignore.case = TRUE)) %>%
  openxlsx::write.xlsx("output/EE_WB_1023.xlsx", sheetName = "EE_WB", firstRow = TRUE, firstCol = TRUE)



```



```{r function}
figure_col<- function(slice,x_title,title,data) {
  data %>%
    group_by({{slice}}) %>%
    dplyr::summarise(amt = sum(`amount(m)`, na.rm = TRUE)) %>%
    ggplot(aes(x = reorder({{slice}},desc(amt)),y = amt)) +
    geom_col( width = 0.5) +
    labs( title = title,
          x = x_title,
          y = "Commitment Amount ($million)") + 
    theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 90))
}

figure_col_n<- function(slice,x_title,title,data) {
  data %>%
    group_by({{slice}}) %>%
    dplyr::summarise(n = n()) %>%
    ggplot(aes(x = reorder({{slice}},desc(n)),y = n)) +
    geom_col( width = 0.5) +
    labs( title = title,
          x = x_title,
          y = "Number of Project") + 
    theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 90))
}


```

## Method:
1. The Energy Efficiency (EE) portfolio is constructed by various approaches, including: 
    + Energy GP portfolio identification and review (mostly WB Lending). 
    + ESMAP portfolio (mostly WB ASA)
    + Product line identification (IFC Sustainable Energy Finance and FI)
    
  
2. The evaluation period is from Fiscal Year 2011 to 2020. EE projects that approved from FY 2011 is scooped in the EE evaluation portfolio. For IFC-AS projects where approval FY is missing, the earliest milestone is regarded as the Approval FY, otherwise left as missing.

3. The commitment amount for WB ASA is estimated by the Energy GP portfolio review, for the ASA projects identified from ESMAP, the preparation cost, if available, is estimated as commitment amount. For the IFC AS project, the commitment amount estimated using the total expenditures for the closed projects and the IFC commitment for active projects. For WB Lending projects, the commitment amount is estimated by the Energy GP portfolio review for components with EE, the disbursement rate is assumed to be 100%. For some IFC IS projects, the commitment amount in the portfolio is different from the documented final value, to be cross-checked and corrected.  

3. The final portfolio is subject to the evaluation team and peer review.  


## Summary Table

```{r wbg_table, echo=FALSE}

table_time <- function(df) {
tab_1 <- df %>%
  group_by(inst) %>%
  summarise(n = n(), cmt = sum(`amount(m)`,na.rm = TRUE)) 
  #%>% mutate(cmt = ifelse(grepl("AS",inst),0,cmt)) 

tab_2 <- tab_1 %>%
  ungroup() %>%
  dplyr::summarise(n = sum(n), cmt = sum(cmt,na.rm = TRUE)) %>%
  mutate(inst = "Total")

tab_1 %>% 
  rbind(tab_2) 
#%>%mutate(cmt = ifelse(grepl("AS",inst),"NA",cmt)) 
}

tab_all <- ee_wbg %>% 
  filter(!is.na(appfy)) %>%
  table_time() %>%
  left_join(
    ee_wbg %>% 
    filter(!is.na(appfy)) %>%
    filter(appfy <= 2010) %>%
    table_time(), by = "inst") %>%
  left_join(
    ee_wbg %>% 
      filter(!is.na(appfy)) %>%
    filter(dplyr::between(appfy,2011,2015)) %>%
    table_time(), by = "inst"
  ) %>%
  left_join(
    ee_wbg %>% 
        filter(!is.na(appfy)) %>%
    filter(dplyr::between(appfy,2016,2020)) %>%
    table_time(), by = "inst"
  ) %>%
  kable( col.names = c("Institution",
                       "n","cmt(`$`m)",
                       "n","cmt(`$`m)",
                       "n","cmt(`$`m)",
                       "n","cmt(`$`m)")) %>%
  kable_styling() %>%
  add_header_above(c(" "=1, "Total" = 2, "<=2010" = 2, 
                     "2011-2015" = 2, "2016-2020" = 2))

tab_master <- ee_wbg %>% 
    filter(!is.na(appfy)) %>%
  filter(dplyr::between(appfy,2011,2020)) %>%
  table_time() %>%
  left_join(
    ee_wbg %>% 
        filter(!is.na(appfy)) %>%
    filter(dplyr::between(appfy,2011,2015)) %>%
    table_time(), by = "inst"
  ) %>%
  left_join(
    ee_wbg %>% 
        filter(!is.na(appfy)) %>%
    filter(dplyr::between(appfy,2016,2020)) %>%
    table_time(), by = "inst"
  ) %>%
  kable( col.names = c("Institution",
                       "n","cmt(`$`m)",
                       "n","cmt(`$`m)",
                       "n","cmt(`$`m)"),
         caption = "Table 1. WBG Energy Efficiency Portfolio Summary") %>%
  kable_styling() %>%
  add_header_above(c(" "=1, "Total" = 2,  
                     "2011-2015" = 2, "2016-2020" = 2))

tab_master
```



```{r wb_table}
#tables

ee_wbg_use <- ee_wbg %>%
  filter(dplyr::between(appfy,2011,2020))

appfy <- ee_wbg_use %>%
  filter(appfy != 0) %>%
  group_by(appfy) %>%
  summarise(amount_total = sum(`amount(m)`,na.rm = TRUE), n_total = n())

income <- ee_wbg_use %>%
  filter(!is.na(income)) %>%
  group_by(income) %>%
  summarise(amount_total = sum(`amount(m)`,na.rm = TRUE)) %>%
  mutate(amount_pct = amount_total/sum(amount_total)*100) %>%
  arrange(amount_pct)

rgn <- ee_wbg_use %>%
  group_by(rgn) %>%
  summarise(amount_total = sum(`amount(m)`,na.rm = TRUE)) %>%
  mutate(amount_pct = amount_total/sum(amount_total)*100) %>%
  arrange(amount_pct)

rgn_compare <-ee_wbg_use %>%
  filter(dplyr::between(appfy,2011,2020)) %>%
  filter(!is.na(ctr_code))%>%
  group_by(ctr_code,rgn)%>%
  dplyr::summarise(n=n(),
                   `amount(m)` = sum(`amount(m)`)) %>%
  inner_join(rise,by="ctr_code") %>%
  left_join(ctr_ptf, by = "ctr_code") %>%
  ungroup %>%
  group_by(rgn) %>%
  summarise(across(c(`amount(m)`,amount_wb,n,n_wb),sum,na.rm = TRUE))%>%
  mutate(wb_amt_rate = `amount(m)`/amount_wb*1e6*100,
         wb_n_rate = n/n_wb*100) 
```



## WBG Energy Efficiency Portfolio by country and project status.

```{r plot_data}

scaleFUN <- function(x) sprintf("%.0f", x)

master <- ee_wbg %>%
  filter(dplyr::between(appfy,2011,2020)) %>%
  mutate(appfy = as.numeric(appfy)) %>%
  group_by(rgn,inst,appfy,income,fcv,lend_grp_wb) %>%
  dplyr::summarise(n = n(), 
                   amt = sum(`amount(m)`, na.rm = TRUE)) %>%
  pivot_longer(c(n,amt),names_to = "unit",values_to = "value") %>%
  mutate(unit = recode(unit,
                       n = "Number of Project (n)",
                       amt = "Commitment Amt. ($m)"))

```


```{r wbg_plot}

slice_col <- function(df,x,title){
  df %>%
  group_by(appfy,inst,unit,{{x}})%>%
  dplyr::summarise(value = sum(value,na.rm = TRUE))%>%
  ggplot(aes(x = appfy,y = value, fill = inst)) +
  geom_col( width = 0.5,colour = "black") +
  labs( title = title,
        x = "Approval FY",
        y = "",
        fill = "Institution",
        caption = "Data Source: IEG, ESMAP") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 90)) +
  facet_grid(cols = vars({{x}}), rows = vars(unit),
             scales = "free_y")  +
  scale_fill_brewer(palette = "Blues") + 
  scale_x_continuous(breaks=seq(2011, 2020, 4)) +
  theme(
  panel.background = element_rect(fill = "white",
                                colour = "white",
                                size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "lightgrey"), 
  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "lightgrey")
  ) 
}
slice_area <- function(df,x,title,tlte_fill){
  df %>%
  #lending only
  filter(!grepl("as",inst,ignore.case = TRUE),
         unit == "Commitment Amt. ($m)",
         {{x}} != "OTH")%>%
  mutate(appfy = as.numeric(appfy)) %>%
  group_by(appfy,{{x}},unit)%>%
  dplyr::summarise(value = sum(value,na.rm = TRUE))%>%
  #start plot
  ggplot(aes(x = appfy,y = value, fill = fct_reorder({{x}},value))) + 
  geom_area(colour = "black") +
  labs( title = title,
        x = "Approval FY",
        y = "Commitment Amt. ($m)",
        fill = tlte_fill,
        caption = "Data Source: IEG, ESMAP") + 
  theme(plot.title = element_text(hjust=0.5)) +
  scale_fill_brewer(palette = "Blues") + 
  scale_x_continuous(breaks=seq(2011, 2020, 4)) +
    theme(
  panel.background = element_rect(fill = "white",
                                colour = "white",
                                size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "lightgrey"), 
  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "lightgrey") 
  )
}
slice_col_1 <- function(df,x,title,tlte_fill){
  df %>%
  #lending only
  filter(!grepl("as",inst,ignore.case = TRUE),
         unit == "Commitment Amt. ($m)",
         {{x}} != "OTH")%>%
  mutate(appfy = as.numeric(appfy)) %>%
  group_by(appfy,{{x}},unit)%>%
  dplyr::summarise(value = sum(value,na.rm = TRUE))%>%
  #start plot
  ggplot(aes(x = appfy,y = value, fill = fct_reorder({{x}},value))) + 
  geom_col(colour = "black") +
  labs( title = title,
        x = "Approval FY",
        y = "Commitment Amt. ($m)",
        fill = tlte_fill,
        caption = "Data Source: IEG, ESMAP") + 
  theme(plot.title = element_text(hjust=0.5)) +
  scale_fill_brewer(palette = "Blues") + 
  scale_x_continuous(breaks=seq(2011, 2020, 4)) +
    theme(
  panel.background = element_rect(fill = "white",
                                colour = "white",
                                size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "lightgrey"), 
  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "lightgrey") 
  )
}
  
#by institution and time
f1 <- slice_area(df=master,x=inst,
                 title="Figure 1. WBG Energy Efficiency Lending Portfolio by Institution",
                 tlte_fill="Institution")


#by region
f2 <- slice_area(df=master,x=rgn,
                 title="Figure 2. WBG Energy Efficiency Lending Portfolio by Region",
                 tlte_fill="Region") +
  labs(caption = "Note: The projects with region tagged as 'OTH' 
       is not included in the figure. \n Data Source: IEG") 

#by income
f3<-master %>%
  ungroup()%>%
  filter(grepl("LIC|LMIC|UMIC|HIC",income)) %>%
  mutate(income = factor(income, levels = c("LIC","LMIC","UMIC","HIC"))) %>%
  slice_col_1(df = ., x = income, 
             title = "Figure 3. WBG Energy Efficiency Lending Portfolio by Income Group",
             tlte_fill = "Income Group") +
  labs(caption = "Note: Regional projects are not included in the figure
       as they are not tagged with country Income Group. \n Data Source: IEG")

#by FCS
f4 <- master %>%
  filter(!is.na(fcv)) %>%
  mutate(fcv = recode(fcv,
                      NO = "Non-FCS",
                      YES = "FCS")) %>%
  slice_col(df = . , x = fcv, title = "Figure 4. WBG Energy Efficiency Portfolio by FCS Status") +
  labs(caption = "Note: Regional projects are not included in the figure
       as they are not tagged with country FCS status. \n Data Source: IEG, ESMAP")

#by lending grp
f5 <- master %>%
  filter(!is.na(lend_grp_wb) & grepl("WB",inst)) %>%
  slice_col(df = ., x = lend_grp_wb, title = "Figure 5. WB Energy Efficiency Portfolio by Lending Group")+
  labs(caption = "Note: Regional projects are not included in the figure
       as they are not tagged with country Lending Group. \n Data Source: IEG, ESMAP")
```


```{r wb_sector}
wb_sector <- ee_wbg %>% #select top 5 sector in the evaluaion period in WB. 
  left_join(sector, by = c("pid"="PROJECTID")) %>%
  rename(sector_major = MAJORSECTOR_NAME) %>%
  distinct()%>%
  filter(dplyr::between(appfy,2011,2020),
         !is.na(sector_major)) %>%
  mutate(appfy = as.character(appfy)) %>%
  group_by(sector_major) %>%
  dplyr::count() %>%
  arrange(-n) %>%
  ungroup() %>%
  mutate(n_rate = n/sum(n)*100) %>%
  top_n(5) %>%
  mutate(sector_main = 1) 

f6_1 <- ee_wbg %>% #add ifc sector as well.
  filter(type == "IS") %>%
  left_join(sector, by = c("pid"="PROJECTID")) %>%
  rename(sector_major = MAJORSECTOR_NAME) %>%
  left_join(wb_sector, by = "sector_major")%>%
  filter(dplyr::between(appfy,2011,2020),
         !is.na(sector_major)) %>%
  mutate(sector_grp = case_when(sector_main == 1 ~ sector_major,
                                TRUE ~ "Other")) %>%
  #filter(sector_grp != "Other") %>%
  group_by(sector_grp,inst,appfy) %>%
  dplyr::summarise(n = n(), 
                   amt = sum(`amount(m)`, na.rm = TRUE)) %>%
  ggplot(aes(x = appfy,y = amt, fill = fct_reorder(sector_grp,amt))) +
  geom_col( width = 0.5, position = "dodge") +
  labs( title = "Figure 6.1. WB Energy Efficiency Lending Portfolio by Sector",
        x = "Approval FY",
        y = "Commitment Amt. ($m)",
        fill = "Major Sector") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 90),
        legend.position="bottom") +
  scale_fill_brewer(palette = "Blues") +
  theme(
  panel.background = element_rect(fill = "white",
                                colour = "white",
                                size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "lightgrey"), 
  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "lightgrey")
  ) +
  labs(caption = "Note: One project could be identified with multiple major sector, 
        Only top five major sectors counted by project number is listed in figure. \n Data Source: IEG")

ifc_sector <- ee_wbg %>% #select top 5 sector in the evaluaion period in IFC. 
  filter(dplyr::between(appfy,2011,2020),
         grepl("IFC",inst, ignore.case = TRUE)) %>%
  group_by(sector_1) %>%
  dplyr::count() %>%
  arrange(-n) %>%
  ungroup() %>%
  mutate(n_rate = n/sum(n)*100) %>%
  top_n(5) %>%
  mutate(sector_main = 1) 

f6_2 <- ee_wbg %>% #add ifc sector as well.
  left_join(ifc_sector, by = "sector_1")%>%
  filter(dplyr::between(appfy,2011,2020),
         grepl("ifc",inst,ignore.case = TRUE)) %>%
  mutate(sector_grp = case_when(sector_main == 1 ~ sector_1,
                                TRUE ~ "Other")) %>%
  #filter(sector_grp != "Other") %>%
  group_by(sector_grp,inst,appfy) %>%
  dplyr::summarise(n = n(), 
                   amt = sum(`amount(m)`, na.rm = TRUE)) %>%
  ggplot(aes(x = appfy,y = amt, fill = fct_reorder(sector_grp,amt))) +
  geom_col( width = 0.5, position = "dodge") +
  labs( title = "Figure 6.2. IFC Energy Efficiency Lending Portfolio by Sector",
        x = "Approval FY",
        y = "Commitment Amt. ($m)",
        fill = "Major Sector") + 
  theme(plot.title = element_text(hjust=0.5),
        axis.text.x = element_text(angle = 90),
        legend.position="bottom") +
  scale_fill_brewer(palette = "Blues") +
    theme(
  panel.background = element_rect(fill = "white",
                                colour = "white",
                                size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "lightgrey"), 
  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "lightgrey")
  ) +
  labs(caption = "Note: One project could be identified with multiple major sector, 
        Only top five major sectors counted by project number is listed in figure, 
        other sectors are categorized as 'Other'. \n Data Source: IEG")
  
```

```{r ctr_indi}

ctr_indi<- ee_wbg %>%
  filter(dplyr::between(appfy,2011,2020)) %>%
  filter(!is.na(ctr_code))%>%
  group_by(ctr_code,rgn)%>%
  dplyr::summarise(n=n(),
                   `amount(m)` = sum(`amount(m)`)) %>%
  inner_join(rise,by="ctr_code") %>%
  left_join(ctr_ptf, by = "ctr_code") %>%
  mutate(wb_amt_rate = `amount(m)`/amount_wb*1e6*100,
         wb_n_rate = n/n_wb*100) 

xline <- median(ctr_indi$score, na.rm = TRUE)
yline <- median(ctr_indi$wb_amt_rate, na.rm = TRUE)

f7 <- ctr_indi %>%
  ggplot(aes(x = score, y = wb_amt_rate, size = wb_n_rate, color = rgn, alpha = 1/5))+
  geom_jitter()+
  geom_text(aes(label=ctr_code),hjust=0, vjust=0) +
  labs(title = "Figure 7. WBG Energy Efficiency Portfolio by Country",
       x = "RISE Energy Efficiency Score (Total)",
       y = "WBG EE Cmt. to WB Country Cmt. (%)",
       color = "Region",
       size = "Proportion by project (n) (%)",
       caption = "Note: The RISE Energy Efficiency score is the total 
       score of 13 RISE Energy Efficiency indicators in 2017.
       The dashlines are the median value of each axis. \n Data Source: IEG, ESMAP") +
  scale_alpha(guide = 'none') +
  geom_hline(yintercept = yline, linetype = "dashed", color = "grey") +
  geom_vline(xintercept = xline, linetype = "dashed", color = "grey") +
  theme(
  panel.background = element_rect(fill = "white",
                                colour = "white",
                                size = 0.5, linetype = "solid"),
  panel.grid.major = element_line(size = 0.5, linetype = 'solid',
                                colour = "lightgrey"), 
  panel.grid.minor = element_line(size = 0.25, linetype = 'solid',
                                colour = "lightgrey")
  ) 



```

## Print to excel


###figures
```{r print_f}


# Create a new xlsx. document

doc <- read_xlsx()

doc <- add_sheet(doc, label = "f1")
doc <- add_sheet(doc, label = "f2")
doc <- add_sheet(doc, label = "f3")
doc <- add_sheet(doc, label = "f4")
doc <- add_sheet(doc, label = "f5")
doc <- add_sheet(doc, label = "f6_1")
doc <- add_sheet(doc, label = "f6_2")
doc <- add_sheet(doc, label = "f7")

doc <- xl_add_vg(doc, sheet = "f1", code = print(f1), 
                 width = 6, height = 6, left = 1, top = 2)
doc <- xl_add_vg(doc, sheet = "f2", code = print(f2), 
                 width = 6, height = 6, left = 1, top = 2)
doc <- xl_add_vg(doc, sheet = "f3", code = print(f3), 
                 width = 6, height = 6, left = 1, top = 2)
doc <- xl_add_vg(doc, sheet = "f4", code = print(f4), 
                 width = 6, height = 6, left = 1, top = 2)
doc <- xl_add_vg(doc, sheet = "f5", code = print(f5), 
                 width = 6, height = 6, left = 1, top = 2)
doc <- xl_add_vg(doc, sheet = "f6_1", code = print(f6_1), 
                 width = 6, height = 6, left = 1, top = 2)
doc <- xl_add_vg(doc, sheet = "f6_2", code = print(f6_2), 
                 width = 6, height = 6, left = 1, top = 2)
doc <- xl_add_vg(doc, sheet = "f7", code = print(f7), 
                 width = 6, height = 6, left = 1, top = 2)

print(doc, target = "output/EE_PRA_f.xlsx")

```

###figure numbers
```{r print_t}
library(officer)
library(rvg)

slice_tab <- function(df,x){
    df %>%
  group_by(appfy,inst,unit,{{x}})%>%
  dplyr::summarise(value = sum(value,na.rm = TRUE))}

tab <- createWorkbook()

add_tab <- function(df, sheet){
  addWorksheet(tab,sheet) 
  writeData(tab,sheet = sheet, x= df)
}

#by institution and time
t1 <- master %>%
  #mutate(appfy = as.numeric(appfy)) %>%
  group_by(appfy,inst,unit)%>%
  dplyr::summarise(value = sum(value,na.rm = TRUE))
add_tab(t1,"t1")

#by region
t2 <- master %>%
  filter(rgn != "OTH") %>%
  slice_tab(df= .,x = rgn)
add_tab(t2,"t2")


#by income
t3<-master %>%
  filter(!is.na(income)) %>%
  mutate(income = factor(income, levels = c("LIC","LMIC","UMIC","HIC"))) %>%
  slice_tab(df = ., x = income)
add_tab(t3,"t3")

   
#by FCS
t4 <- master %>%
  filter(!is.na(fcv)) %>%
  mutate(fcv = recode(fcv,
                      NO = "Non-FCS",
                      YES = "FCS")) %>%
  slice_tab(df = . , x = fcv)
add_tab(t4,"t4")

#by lending grp
t5 <- master %>%
  filter(!is.na(fcv) & grepl("WB",inst)) %>%
  slice_tab(df = ., x = lend_grp_wb)
add_tab(t5,"t5")

#sector
t6_1 <- ee_wbg %>%
  left_join(sector, by = c("pid"="PROJECTID")) %>%
  rename(sector_major = MAJORSECTOR_NAME) %>%
  left_join(wb_sector, by = "sector_major")%>%
  filter(dplyr::between(appfy,2011,2020),
         !is.na(sector_major)) %>%
  mutate(sector_grp = case_when(sector_main == 1 ~ sector_major,
                                TRUE ~ "Other")) %>%
  group_by(sector_grp,inst,appfy) %>%
  dplyr::summarise(n = n(), 
                   amt = sum(`amount(m)`, na.rm = TRUE)) %>%
  pivot_longer(c(n,amt),names_to = "unit",values_to = "value") %>%
  mutate(unit = recode(unit,
                       n = "Number of Project (n)",
                       amt = "Commitment Amt. ($m)"))
add_tab(t6_1,"t6_1")

t6_2 <- ee_wbg %>%
  left_join(ifc_sector, by = "sector_1")%>%
  filter(dplyr::between(appfy,2011,2020),
         grepl("ifc",inst,ignore.case = TRUE)) %>%
  mutate(sector_grp = case_when(sector_main == 1 ~ sector_1,
                                TRUE ~ "Other")) %>%
  group_by(sector_grp,inst,appfy) %>%
  dplyr::summarise(n = n(), 
                   amt = sum(`amount(m)`, na.rm = TRUE)) %>%
  pivot_longer(c(n,amt),names_to = "unit",values_to = "value") %>%
  mutate(unit = recode(unit,
                       n = "Number of Project (n)",
                       amt = "Commitment Amt. ($m)"))
add_tab(t6_2,"t6_2")

#ctr
t7<-ctr_indi
add_tab(t7,"t7")

saveWorkbook(tab, "output/EE_PRA.xlsx", overwrite = TRUE)
          

```
